---
title: My dynamic report
author: "Spencer Reinsfield - srei868"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: 'Ariel', sans-serif;
  color: #000000;
  background-color: #ECECEC;
  margin: 10px;
  padding: 10px;
  font-size: 17px;
}
h1 {
  font-family: 'Ariel', sans-serif;
  font-weight: bold;
  text-decoration: underline;
}
```

## Using R Studio to analyse coffee shop order data

To explore the data that was collected, we need to log the data with renamed csv file variables. The file that performs this task is exploration.R.

Now that this is complete, we can add some code to the end of exploration.R to produce bar chart and summary values.

# What is the most popular coffee drink at the University of Auckland's Ora Cafe?

Using the data set, we will generate a bar chart to compare the number of orders of each drink that was ordered.

```{r, eval=TRUE, echo=FALSE}
library(tidyverse)
library(magick)
logged_data <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRnfLyTKVyX5-jXaBNIPl004RH4PzWjIu-nP7fWblJZMbMi61H8gjTIXQYr0es24LiAs4lJfQm9K-kd/pub?gid=415879415&single=true&output=csv"
logged_data <- read_csv(logged_data)

# Change the variable names because they would be a question without rename()
logged_data_renamed <- logged_data %>%
  rename(temperature = 2,
         drink_name = 3,
         drink_type = 4,
         size = 5,
         time_to_make = 6)

# Create the plots and values
logged_data_renamed %>%
  ggplot() + geom_bar(aes(x = drink_name)) + labs(title = "Number of Coffee Orders")
names_vector <- logged_data_renamed$drink_name
most_observed_drink <- sum(names_vector == "Flat White")
paste0(most_observed_drink, " orders were a Flat White.")

```

According to the bar chart, the most popular coffee drink at the University of Auckland's Ora Cafe is the Flat White. This makes sense as the Flat White is an especially popular in Australia and New Zealand as a whole.

# Is it more likely that an order at the University of Auckland's Ora Cafe is takeaway?

```{r, eval=TRUE, echo=FALSE}
logged_data_renamed %>%
  ggplot() + geom_bar(aes(x = drink_type)) + labs(title = "Coffee Orders that were Takeaway or Dine In")
# table() is a function taught in STATS 20x
table(logged_data_renamed$drink_type)
num_takeaway <- sum(logged_data_renamed$drink_type == "Takeaway")
num_dine_in <- sum(logged_data_renamed$drink_type == "Dine in")
paste0("The data set observed ", num_takeaway, " takeaway orders and ", num_dine_in, " dine in orders.")
```

# Is it more likely that an order at the University of Auckland's Ora Cafe is a large size?

```{r, eval=TRUE, echo=FALSE}
logged_data_renamed %>%
  ggplot() + geom_bar(aes(x = size)) + labs(title = "Coffee Orders that were Medium or Large")
# table() is a function taught in STATS 20x
table(logged_data_renamed$size)
```

Now that we have explored interesting components about our categorical variables, lets analyse the data sets only numeric value, time_to_make. First let's check the mean time_to_make and minimum time_to_make.

# How long on average does it take to complete a coffee order at the University of Auckland's Ora Cafe?

```{r, eval=TRUE, echo=FALSE}
# Find the mean time_to_make
num_observations <- logged_data_renamed$time_to_make %>%
  length()
computed_mean <- logged_data_renamed$time_to_make %>%
  mean() %>% round(1)
paste0("The mean computing time to complete a coffee order from ", num_observations, " observations recorded was ", computed_mean, " seconds.")
```

The summary output for the mean time to complete a coffee order may change as more observations are recorded in the data set.

```{r, eval=TRUE, echo=FALSE}
# Find the lowest recorded instance of time_to_make
num_observations <- logged_data_renamed$time_to_make %>%
  length()
computed_min <- logged_data_renamed$time_to_make %>%
  min() %>% round(1)
paste0("The minimum computing time to complete a coffee order from ", num_observations, " observations recorded was ", computed_min, " seconds.")
```

The summary output for the minimum time to complete a coffee order may change as more observations are recorded in the data set.

This minimum value makes me wonder how the mean time it takes to complete a hot coffee order compares to the mean time it takes to complete a cold coffee order.

```{r, eval=TRUE, echo=FALSE}
# Compute mean time given hot order and mean time given cold order
mean_given_hot <- logged_data_renamed$time_to_make[logged_data_renamed$temperature == "Hot"] %>%
  mean() %>% round(1)
mean_given_cold <- logged_data_renamed$time_to_make[logged_data_renamed$temperature == "Cold"] %>%
  mean() %>% round(1)
paste0("Given that the coffee order was hot, the mean computing time to complete a coffee order from ", num_observations, " observations recorded was ", mean_given_hot, " seconds.")
paste0("Given that the coffee order was cold, the mean computing time to complete a coffee order from ", num_observations, " observations recorded was ", mean_given_cold, " seconds.")
```

According to the summary outputs the mean time it takes to complete a hot coffee order is greater than the mean time it takes to complete a cold coffee order. This makes sense since in most hot coffee orders, the barista needs to steam milk which take more than just pouring cold milk into a cold drink order. That being said, the means can change as more observations are recorded in the data set.
